---
title: "TERGM for Somali IDP networks"
output: tergm_notebook
---

Load libraries

```{r}
library("tergm")
library("texreg")
#library("xergm")
#library("btergm")
library("tsna")
library("ndtv")
library("statnet")
library("htmlwidgets")
library("latticeExtra")
library("tidyverse")
library("igraph")
library("fs")
library("tictoc")
library("RSiena")
```

Load IDP flow data

```{r}
# Laptop directory
# dir.data <- "C:/Users/17654/Dropbox (UFL)/Woi Sok Tony Oh/HMEIPostdoc/research/SomIDPModel/data"
# Office PC directory
 dir.data <- "C:/Users/Woi Sok Oh/Documents/Sourcetree/SomERGM/data"
fls <- dir_ls(dir.data)
fls <- fls |> str_subset("idp")
out <- map(fls, read_csv, skip = 0, col_names = 1:74)
class(out) # list
length(out) # 60
out <- map(out, function(x) as.matrix(x))
for (k in 1:60){diag(out[[k]]) <- 0}
out2 <- out[13:60]
```

Load attribute data

```{r}
fls <- dir_ls(dir.data)
fls <- fls |> str_subset("var")
att <- map(fls, read_csv)
# distance
setwd(dir.data)
distance <- read_csv("distance.csv",col_names =FALSE)
region <- read_csv("regions.csv",col_names =FALSE)
```

Link attributes to nodes

```{r}
nets <- list()
for (i in 1:60){
  # att
  att2 <- map2(.x = att, .y = i, function(x,y) {x$month <- y; return(x)})
  att3 <-bind_rows(att2)
  dat <- att3 |> group_by(id) |>
    summarize(
      tot_con_occ = tot_con_occ,
      tot_con_fat = tot_con_fat,
      batt_occ = batt_occ,
      batt_fat = batt_fat,
      civi_occ = civi_occ,
      civi_fat = civi_fat,
      expl_occ = expl_occ,
      expl_fat = expl_fat,
      prot_occ = prot_occ,
      prot_fat = prot_fat,
      riot_occ = riot_occ,
      riot_fat = riot_fat,
      stra_occ = stra_occ,
      stra_fat = stra_fat,
      spi0 = spi0,
      spi1 = spi1,
      spi2 = spi2,
      spi3 = spi3,
      dry = dry,
      mod_dry = mod_dry,
      ext_dry = ext_dry,
      wet = wet,
      mod_wet = mod_wet,
      ext_wet = ext_wet,
      pop = pop,
      chirps0 = chirps0,
      chirps1 = chirps1,
      chirps2 = chirps2,
      chirps3 = chirps3,
      ndvi0 = ndvi0,
      ndvi1 = ndvi1,
      ndvi2 = ndvi2,
      ndvi3 = ndvi3,
      avgrain0 = avgrain0,
      avgrain1 = avgrain1,
      avgrain2 = avgrain2,
      avgrain3 = avgrain3,
      norain0 = norain0,
      norain1 = norain1,
      norain2 = norain2,
      norain3 = norain3,
      clan = clans,
      alsha_occ = alsha_occ,
      alsha_fat = alsha_fat,
      fatcon_occ = fatcon_occ,
      fatcon_fat = fatcon_fat,
      temp0 = temp0,
      temp1 = temp1,
      temp2 = temp2,
      temp3 = temp3,
      pdi0 = pdi0,
      pdi1 = pdi1,
      pdi2 = pdi2,
      pdi3 = pdi3,
      tdi0 = tdi0,
      tdi1 = tdi1,
      tdi2 = tdi2,
      tdi3 = tdi3,
      vdi0 = vdi0,
      vdi1 = vdi1,
      vdi2 = vdi2,
      vdi3 = vdi3,
      cdi0 = cdi0,
      cdi1 = cdi1,
      cdi2 = cdi2,
      cdi3 = cdi3
      
    )
  # build a network
  net <- network(out[[i]],directed = TRUE,loops = FALSE,matrix.type="adjacency")
  net %e% "flow" <- out[[i]] 
  net %e% "distance" <- distance
  
  net %v% "tot_con_occ" <- dat$tot_con_occ
  net %v% "tot_con_fat" <- dat$tot_con_fat
  net %v% "batt_occ" <- dat$batt_occ
  net %v% "batt_fat" <- dat$batt_fat
  net %v% "civi_occ" <- dat$civi_occ
  net %v% "civi_fat" <- dat$civi_fat
  net %v% "expl_occ" <- dat$expl_occ
  net %v% "expl_fat" <- dat$expl_fat
  net %v% "prot_occ" <- dat$prot_occ
  net %v% "prot_fat" <- dat$prot_fat
  net %v% "riot_occ" <- dat$riot_occ
  net %v% "riot_fat" <- dat$riot_fat
  net %v% "stra_occ" <- dat$stra_occ
  net %v% "stra_fat" <- dat$stra_fat
  net %v% "spi0" <- dat$spi0
  net %v% "spi1" <- dat$spi1
  net %v% "spi2" <- dat$spi2
  net %v% "spi3" <- dat$spi3
  net %v% "dry" <- dat$dry
  net %v% "mod_dry" <- dat$mod_dry
  net %v% "ext_dry" <- dat$ext_dry
  net %v% "wet" <- dat$wet
  net %v% "mod_wet" <- dat$mod_wet
  net %v% "ext_wet" <- dat$ext_wet
  net %v% "pop" <- dat$pop
  net %v% "chirps0" <- dat$chirps0
  net %v% "chirps1" <- dat$chirps1
  net %v% "chirps2" <- dat$chirps2
  net %v% "chirps3" <- dat$chirps3
  net %v% "ndvi0" <- dat$ndvi0
  net %v% "ndvi1" <- dat$ndvi1
  net %v% "ndvi2" <- dat$ndvi2
  net %v% "ndvi3" <- dat$ndvi3
  net %v% "avgrain0" <- dat$avgrain0
  net %v% "avgrain1" <- dat$avgrain1
  net %v% "avgrain2" <- dat$avgrain2
  net %v% "avgrain3" <- dat$avgrain3
  net %v% "norain0" <- dat$norain0
  net %v% "norain1" <- dat$norain1
  net %v% "norain2" <- dat$norain2
  net %v% "norain3" <- dat$norain3
  net %v% "clan" <- dat$clan
  net %v% "alsha_occ" <- dat$alsha_occ
  net %v% "alsha_fat" <- dat$alsha_fat
  net %v% "fatcon_occ" <- dat$fatcon_occ
  net %v% "fatcon_fat" <- dat$fatcon_fat
  net %v% "temp0" <- dat$temp0
  net %v% "temp1" <- dat$temp1
  net %v% "temp2" <- dat$temp2
  net %v% "temp3" <- dat$temp3
  net %v% "pdi0" <- dat$pdi0
  net %v% "pdi1" <- dat$pdi1
  net %v% "pdi2" <- dat$pdi2
  net %v% "pdi3" <- dat$pdi3
  net %v% "tdi0" <- dat$tdi0
  net %v% "tdi1" <- dat$tdi1
  net %v% "tdi2" <- dat$tdi2
  net %v% "tdi3" <- dat$tdi3
  net %v% "vdi0" <- dat$vdi0
  net %v% "vdi1" <- dat$vdi1
  net %v% "vdi2" <- dat$vdi2
  net %v% "vdi3" <- dat$vdi3
  net %v% "cdi0" <- dat$cdi0
  net %v% "cdi1" <- dat$cdi1
  net %v% "cdi2" <- dat$cdi2
  net %v% "cdi3" <- dat$cdi3
  net %v% "region" <- region
  nets[[i]] <- net
}
```

Develop a ERGM

```{r}


```



Develop a TERGM

Initial model

```{r}
tic()
nw.fit.fp1 <- tergm(nets ~ edges,
                     estimate = "CMLE",
                     times = c(1:60)
)
toc() # 10.79 sec in laptop
summary(nw.fit.fp1)

tic()
nw.fit.fp1_2 <- tergm(nets ~ edges + transitiveties + mutual,
                     estimate = "CMLE",
                     times = c(1:60)
)
toc() # 10.79 sec in laptop
summary(nw.fit.fp1_2)

```

Model 2: Conflict diff model

```{r}
tic()
nw.fit.fp2 <- tergm(nets ~ edges + diff("tot_con_occ") +diff("tot_con_fat") + diff("alsha_occ") + diff("alsha_fat") + diff("fatcon_occ") + diff("fatcon_fat"),
                     estimate = "CMLE",
                     times = c(1:60)
)
toc() # 8.74 sec in laptop
summary(nw.fit.fp2)
```

Model 3: climate variable diff model
Environmental/Climate data (number stands for time lag, e.g., 1 means that it is monthly data of a previous year)
- SPI : Standard precipitation index (based on CHIRPS precipitation data in this case)
- CHIRPS : Monthly precipitation data
- NDVI : Normalized Difference Vegetation Index
- norain : Percentage of no-rainfall days each month (based on CHIRPS data)
- avgrain : monthly precipitation / rainfall days

```{r}
tic()
nw.fit.fp3 <- tergm(nets ~ edges+diff("spi0")+diff("spi1")+diff("spi2")+diff("spi3")+diff("chirps0")+diff("chirps1")+diff("chirps2")+diff("chirps3")+diff("ndvi0")+diff("ndvi1")+diff("ndvi2")+diff("ndvi3")+diff("norain0")+diff("norain1")+diff("norain2")+diff("norain3")+diff("avgrain0")+diff("avgrain1")+diff("avgrain2")+diff("avgrain3")+diff("temp0")+diff("temp1")+diff("temp2")+diff("temp3")+diff("pdi0")+diff("pdi1")+diff("pdi2")+diff("pdi3")+diff("tdi0")+diff("tdi1")+diff("tdi2")+diff("tdi3")+diff("vdi0")+diff("vdi1")+diff("vdi2")+diff("vdi3")+diff("cdi0")+diff("cdi1")+diff("cdi2")+diff("cdi3"),
                     estimate = "CMLE",
                     times = c(1:60)
)
toc() # 11.67 sec in laptop
summary(nw.fit.fp3)
```

Model 4: Social model

```{r}
tic()
nw.fit.fp4 <- tergm(nets ~ edges+nodematch("clan")+diff("pop"),
                     estimate = "CMLE",
                     times = c(1:60)
)
toc() # 11.67 sec in laptop
summary(nw.fit.fp4)
```




Separable model

```{r}
tic()
nw.fit.sfp1 <- tergm(nets ~ 
                       Form(~edges) +
                       Persist(~edges),
                     estimate = "CMLE",
                     times = c(1:60)
)
toc() # 11.45 sec in laptop
summary(nw.fit.sfp1)
```

Separable Model 2: mutual and transitive triads

```{r}
tic()
nw.fit.sfp2 <- tergm(nets ~
                      Form(~edges+mutual+transitiveties) +
                      Persist(~edges+mutual+transitiveties),
                    estimate = "CMLE",
                    times = c(1:60)
)
toc() # 1560.03 sec in laptop
summary(nw.fit.sfp2)
```

Separable Model 3: differences of conflict attributes

```{r}
# occurrence
tic()
nw.fit.sfp3 <- tergm(nets ~
                      Form(~edges+diff("tot_con_occ")+diff("batt_occ")+diff("civi_occ")+diff("expl_occ")+diff("prot_occ")+diff("riot_occ")+diff("stra_occ")+diff("tot_con_fat")+diff("batt_fat")+diff("civi_fat")+diff("expl_fat")+diff("prot_fat")+diff("riot_fat")+diff("stra_fat")) +
                      Persist(~edges+diff("tot_con_occ")+diff("batt_occ")+diff("civi_occ")+diff("expl_occ")+diff("prot_occ")+diff("riot_occ")+diff("stra_occ")+diff("tot_con_fat")+diff("batt_fat")+diff("civi_fat")+diff("expl_fat")+diff("prot_fat")+diff("riot_fat")+diff("stra_fat")),
                    estimate = "CMLE",
                    times = c(1:60)
)
toc() # 16.12 sec in laptop
summary(nw.fit.sfp3)

```

Model 4: differences of precipitation attributes

```{r}
tic()
nw.fit.sfp4 <- tergm(nets ~
                      Form(~edges+diff("spi0")+diff("spi1")+diff("spi2")+diff("spi3")+diff("chirps0")+diff("chirps1")+diff("chirps2")+diff("chirps3")+diff("ndvi0")+diff("ndvi1")+diff("ndvi2")+diff("ndvi3")+diff("norain0")+diff("norain1")+diff("norain2")+diff("norain3")+diff("avgrain0")+diff("avgrain1")+diff("avgrain2")+diff("avgrain3")) +
                      Persist(~edges+diff("spi0")+diff("spi1")+diff("spi2")+diff("spi3")+diff("chirps0")+diff("chirps1")+diff("chirps2")+diff("chirps3")+diff("ndvi0")+diff("ndvi1")+diff("ndvi2")+diff("ndvi3")+diff("norain0")+diff("norain1")+diff("norain2")+diff("norain3")+diff("avgrain0")+diff("avgrain1")+diff("avgrain2")+diff("avgrain3")),
                    estimate = "CMLE",
                    times = c(1:100)
)
toc() # 27.51 sec in laptop
summary(nw.fit.sfp4)
```

Model 5: 


Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
