---
title: "ERGM for Somali IDP networks"
output: ergm_notebook
---

Load libraries

```{r}
library(tidyverse)
library(fs)
library(network)
library(ergm)
library(ergm.count)
library(tictoc)
```

Load IDP data
```{r}
# Office PC directory
 dir.data <- "C:/Users/Woi Sok Oh/Documents/Sourcetree/SomERGM/data"
# Laptop directory
# dir.data <- "C:/Users/17654/Dropbox (UFL)/Woi Sok Tony Oh/HMEIPostdoc/research/SomIDPModel/data"
fls <- dir_ls(dir.data)
fls
fls <- fls |> str_subset("2017") |> str_subset("idp")
fls
out <- map(fls, read_csv, skip = 0, col_names = 1:74)
class(out)
length(out)
#out <- map2(.x = out, .y = 1:12, function(x,y) {x$month <- y; return(x)})
out <- map(out, function(x) as.matrix(x))

mat <- out[[1]] + out[[2]] + out[[3]] + out[[4]] + out[[5]] + out[[6]] + out[[7]] + out[[8]] + out[[9]] + out[[10]] + out[[11]] + out[[12]]
diag(mat) <- 0
# urban->urban
fls <- dir_ls(dir.data)
fls
fls <- fls |> str_subset("2017") |> str_subset("uu") 
fls
out <- map(fls, read_csv, skip = 0, col_names = 1:74)
class(out)
length(out)
#out <- map2(.x = out, .y = 1:12, function(x,y) {x$month <- y; return(x)})
out <- map(out, function(x) as.matrix(x))

mat_uu <- out[[1]] + out[[2]] + out[[3]] + out[[4]] + out[[5]] + out[[6]] + out[[7]] + out[[8]] + out[[9]] + out[[10]] + out[[11]] + out[[12]]
diag(mat_uu) <- 0

# urban->rural
fls <- dir_ls(dir.data)
fls
fls <- fls |> str_subset("2017") |> str_subset("ur") 
fls
out <- map(fls, read_csv, skip = 0, col_names = 1:74)
class(out)
length(out)
#out <- map2(.x = out, .y = 1:12, function(x,y) {x$month <- y; return(x)})
out <- map(out, function(x) as.matrix(x))

mat_ur <- out[[1]] + out[[2]] + out[[3]] + out[[4]] + out[[5]] + out[[6]] + out[[7]] + out[[8]] + out[[9]] + out[[10]] + out[[11]] + out[[12]]
diag(mat_ur) <- 0

# rural->urban
fls <- dir_ls(dir.data)
fls
fls <- fls |> str_subset("2017") |> str_subset("ru") 
fls
out <- map(fls, read_csv, skip = 0, col_names = 1:74)
class(out)
length(out)
#out <- map2(.x = out, .y = 1:12, function(x,y) {x$month <- y; return(x)})
out <- map(out, function(x) as.matrix(x))

mat_ur <- out[[1]] + out[[2]] + out[[3]] + out[[4]] + out[[5]] + out[[6]] + out[[7]] + out[[8]] + out[[9]] + out[[10]] + out[[11]] + out[[12]]
diag(mat_ru) <- 0

# rural->rural
fls <- dir_ls(dir.data)
fls
fls <- fls |> str_subset("2017") |> str_subset("rr") 
fls
out <- map(fls, read_csv, skip = 0, col_names = 1:74)
class(out)
length(out)
#out <- map2(.x = out, .y = 1:12, function(x,y) {x$month <- y; return(x)})
out <- map(out, function(x) as.matrix(x))

mat_rr <- out[[1]] + out[[2]] + out[[3]] + out[[4]] + out[[5]] + out[[6]] + out[[7]] + out[[8]] + out[[9]] + out[[10]] + out[[11]] + out[[12]]
diag(mat_rr) <- 0

# Previous year IDP flows
fls <- dir_ls(dir.data)
fls
fls <- fls |> str_subset("2016") |> str_subset("idp")
fls
out <- map(fls, read_csv, skip = 0, col_names = 1:74)
class(out)
length(out)
#out <- map2(.x = out, .y = 1:12, function(x,y) {x$month <- y; return(x)})
out <- map(out, function(x) as.matrix(x))

net2016 <- out[[1]] + out[[2]] + out[[3]] + out[[4]] + out[[5]] + out[[6]] + out[[7]] + out[[8]] + out[[9]] + out[[10]] + out[[11]] + out[[12]]
diag(net2016) <- 0
net2016 <- 1*(net2016 > 0)

# uu
fls <- dir_ls(dir.data)
fls
fls <- fls |> str_subset("2016") |> str_subset("uu")
fls
out <- map(fls, read_csv, skip = 0, col_names = 1:74)
class(out)
length(out)
#out <- map2(.x = out, .y = 1:12, function(x,y) {x$month <- y; return(x)})
out <- map(out, function(x) as.matrix(x))

net2016_uu <- out[[1]] + out[[2]] + out[[3]] + out[[4]] + out[[5]] + out[[6]] + out[[7]] + out[[8]] + out[[9]] + out[[10]] + out[[11]] + out[[12]]
diag(net2016_uu) <- 0
net2016_uu <- 1*(net2016_uu > 0)
# ur
fls <- dir_ls(dir.data)
fls
fls <- fls |> str_subset("2016") |> str_subset("ur")
fls
out <- map(fls, read_csv, skip = 0, col_names = 1:74)
class(out)
length(out)
#out <- map2(.x = out, .y = 1:12, function(x,y) {x$month <- y; return(x)})
out <- map(out, function(x) as.matrix(x))

net2016_ur <- out[[1]] + out[[2]] + out[[3]] + out[[4]] + out[[5]] + out[[6]] + out[[7]] + out[[8]] + out[[9]] + out[[10]] + out[[11]] + out[[12]]
diag(net2016_ur) <- 0
net2016_ur <- 1*(net2016_ur > 0)
# ru
fls <- dir_ls(dir.data)
fls
fls <- fls |> str_subset("2016") |> str_subset("ru")
fls
out <- map(fls, read_csv, skip = 0, col_names = 1:74)
class(out)
length(out)
#out <- map2(.x = out, .y = 1:12, function(x,y) {x$month <- y; return(x)})
out <- map(out, function(x) as.matrix(x))

net2016_ru <- out[[1]] + out[[2]] + out[[3]] + out[[4]] + out[[5]] + out[[6]] + out[[7]] + out[[8]] + out[[9]] + out[[10]] + out[[11]] + out[[12]]
diag(net2016_ru) <- 0
net2016_ru <- 1*(net2016_ru > 0)
# rr
fls <- dir_ls(dir.data)
fls
fls <- fls |> str_subset("2016") |> str_subset("rr")
fls
out <- map(fls, read_csv, skip = 0, col_names = 1:74)
class(out)
length(out)
#out <- map2(.x = out, .y = 1:12, function(x,y) {x$month <- y; return(x)})
out <- map(out, function(x) as.matrix(x))

net2016_rr <- out[[1]] + out[[2]] + out[[3]] + out[[4]] + out[[5]] + out[[6]] + out[[7]] + out[[8]] + out[[9]] + out[[10]] + out[[11]] + out[[12]]
diag(net2016_rr) <- 0
net2016_rr <- 1*(net2016_rr > 0)

```

Load attribute data
```{r}
## attributes

fls <- dir_ls(dir.data)
fls

fls <- fls |> str_subset("2017") |> str_subset("var")

out <- map(fls, read_csv)
out <- map2(.x = out, .y = 1:12, function(x,y) {x$month <- y; return(x)})

out

out <-bind_rows(out)
setwd(dir.data)
distance <- read_csv("distance.csv",col_names =FALSE)
distance <- as.matrix(distance)
```

Build network

```{r}
dat <- out |> group_by(id) |>
  summarize(
    tot_con_occ = sum(tot_con_occ),
    tot_con_fat = sum(tot_con_fat),
    alsha_occ = sum(alsha_occ),
    alsha_fat = sum(alsha_fat),
    fatcon_occ = sum(fatcon_occ),
    fatcon_fat = sum(fatcon_fat),
    spi_m = mean(spi0),
    spi_max = max(spi0),
    spi_min = min(spi0),
    chirps_m = mean(chirps0),
    chirps_max = max(chirps0),
    chirps_min = min(chirps0),
    ndvi_m = mean(ndvi0),
    ndvi_max = max(ndvi0),
    ndvi_min = min(ndvi0),
    avgrain_m = mean(avgrain0),
    avgrain_max = max(avgrain0),
    avgrain_min = min(avgrain0),
    norain_m = mean(norain0),
    norain_max = max(norain0),
    norain_min = min(norain0),
    clan = clans,
    temp_m = mean(temp0),
    temp_max = max(temp0),
    temp_min = min(temp0),
    pdi_m = mean(pdi0),
    pdi_max = max(pdi0),
    pdi_min = min(pdi0),
    tdi_m = mean(tdi0),
    tdi_max = max(tdi0),
    tdi_min = min(tdi0),
    vdi_m = mean(vdi0),
    vdi_max = max(vdi0),
    vdi_min = min(vdi0),
    pop14 = mean(pop14),
    urban = mean(popurban14),
    rural = mean(poprural14),
    region = mean(region),
    urbanrural = mean(popurban14)/mean(poprural14)
  )
```

```{r}
net <- network(mat, directed = TRUE)
net
net %e% "flow" <- mat
net %e% "net2016" <- net2016
net %e% "distance" <- distance
net %v% "tot_con_occ" <- dat$tot_con_occ
net %v% "tot_con_fat" <- dat$tot_con_fat
net %v% "alsha_occ" <- dat$alsha_occ
net %v% "alsha_fat" <- dat$alsha_fat
net %v% "fatcon_occ" <- dat$fatcon_occ
net %v% "fatcon_fat" <- dat$fatcon_fat
net %v% "spi_m" <- dat$spi_m
net %v% "spi_max" <- dat$spi_max
net %v% "spi_min" <- dat$spi_min
net %v% "chirps_m" <- dat$chirps_m
net %v% "chirps_max" <- dat$chirps_max
net %v% "chirps_min" <- dat$chirps_min
net %v% "ndvi_m" <- dat$ndvi_m
net %v% "ndvi_max" <- dat$ndvi_max
net %v% "ndvi_min" <- dat$ndvi_min
net %v% "avgrain_m" <- dat$avgrain_m
net %v% "avgrain_max" <- dat$avgrain_max
net %v% "avgrain_min" <- dat$avgrain_min
net %v% "norain_m" <- dat$norain_m
net %v% "norain_max" <- dat$norain_max
net %v% "norain_min" <- dat$norain_min
net %v% "clan" <- dat$clan
net %v% "temp_m" <- dat$temp_m
net %v% "temp_max" <- dat$temp_max
net %v% "temp_min" <- dat$temp_min
net %v% "pdi_m" <- dat$pdi_m
net %v% "pdi_max" <- dat$pdi_max
net %v% "pdi_min" <- dat$pdi_min
net %v% "tdi_m" <- dat$tdi_m
net %v% "tdi_max" <- dat$tdi_max
net %v% "tdi_min" <- dat$tdi_min
net %v% "vdi_m" <- dat$vdi_m
net %v% "vdi_max" <- dat$vdi_max
net %v% "vdi_min" <- dat$vdi_min
net %v% "pop14" <- dat$pop14
net %v% "urban" <- dat$urban
net %v% "rural" <- dat$rural
net %v% "region" <- dat$region
net %v% "urbanrural" <- dat$urbanrural
net
```

```{r}
# observed distribution of triangles
summary(net~triadcensus)
```
Model I: Null model

```{r}
f0 <- ergm(net ~ edges)
summary(f0)
```
Model II: Network model with transitivity, mutuality, cyclicality


```{r}
f1 <- ergm(net ~ edges+transitiveties+mutual+cyclicalties)
summary(f1)
```

Model III: Addition of edge attributes
  distance - geodesic distance
  net2016 - IDP routes of the previous year, 2016

```{r}
f2 <- ergm(net ~ edges+transitiveties+mutual+cyclicalties+edgecov(distance)+edgecov(net2016))
summary(f2)
```

Model IV: Social model
  alsha_occ - occurrence number of Al-Shabaab-related conflict events
  urbanrural - urban population / rural population

```{r}
f3 <- ergm(net ~ edges+transitiveties+mutual+cyclicalties+dgwdsp(1, fixed = TRUE, cutoff = 7, type = c("OSP"))+edgecov(distance)+edgecov(net2016)+nodeocov("alsha_occ")+diff("urbanrural"))
summary(f3)
```

Model V: P-model (precipitation model)
  pdi_m - Average Precipitation Drought Index in 2017 (includes both drought intensity by rainfalls and consecutive dryness) -> the higher the better
  chirps_m - Average precipitation in 2017 (includes only precipitation intensity) -> the higher the better

```{r}
f4 <- ergm(net ~ edges+transitiveties+mutual+cyclicalties+dgwdsp(1, fixed = TRUE, cutoff = 7, type = c("OSP"))+edgecov(distance)+edgecov(net2016)+nodeocov("alsha_occ")+diff("urbanrural")+nodeocov("pdi_m")+nodeicov("pdi_m")+nodeocov("chirps_m")+nodeicov("chirps_m"))
summary(f4)
```

Model VI: T-Model (Temperature model)
  tdi_m - Average Temperature Drought Index in 2017 (includes both drought intensity by temperature and consecutive high temperature) -> the higher the better
  temp_m - Average temperature in 2017 (includes only degree of temperature) -> the lower the better

```{r}
f5 <- ergm(net ~ edges+transitiveties+mutual+cyclicalties+dgwdsp(1, fixed = TRUE, cutoff = 7, type = c("OSP"))+edgecov(distance)+edgecov(net2016)+nodeocov("alsha_occ")+diff("urbanrural")+nodeocov("tdi_m")+nodeicov("tdi_m")+nodeocov("temp_m")+nodeicov("temp_m"))
summary(f5)
```

Model VII: V-Model (Vegetation Model)
  vdi_m - Average Vegetation Drought Index in 2017 (includes both drought intensity by vegetation and consecutive low vegetation) -> the higher the better
  ndvi_m - Average vegetation in 2017 (includes only degree of NDVI) -> the higher the better

```{r}
f6 <- ergm(net ~ edges+transitiveties+mutual+cyclicalties+dgwdsp(1, fixed = TRUE, cutoff = 7, type = c("OSP"))+edgecov(distance)+edgecov(net2016)+nodeocov("alsha_occ")+diff("urbanrural")+nodeocov("vdi_m")+nodeicov("vdi_m")+nodeocov("ndvi_m")+nodeicov("ndvi_m"))
summary(f6)
```

```{r}
f7 <- ergm(net ~ edges+transitiveties+mutual+cyclicalties+dgwdsp(1, fixed = TRUE, cutoff = 7, type = c("OSP"))+edgecov(distance)+edgecov(net2016)+nodeocov("alsha_occ")+diff("urbanrural")+diff("pdi_m")+diff("tdi_m")+diff("vdi_m"))
summary(f7)
```

```{r}

```